\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------AWAL-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Muhammad Hafiz Tsalavin}} & Email : \href{mailto:hafiztsalavin@gmail.com}{hafiztsalavin@gmail.com}\\
  \url {} & LinkedIn: \href {https://www.linkedin.com/in/hafiztsalavin/} {linkedin.com/in/hafiztsalavin} \\
  \url {} & Github: \href {https://github.com/hafiztsalavin} {github.com/hafiztsalavin} \\
\end{tabular*}

%-----------tujuan-----------------
\section{Objective}
{\bf To obtain an internship in which I can assist on commercial team using my technical background as well as organizational and leadership skills.}


%-----------sekolah-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Diponegoro University}{Semarang, Indonesia}
      {Bachelor of Engineering in Computer Engineering}{}
    \item {\bf Technical Skills and Coursework:}
    \vspace{-.3cm}
      \resumeItemListStart
        \item{
         \textbf{Systems}{: Linux, Windows}
        }
        \vspace{-.2cm}
        \item{
         \textbf{Packages}{: Ms.Office, Libre Office, Corel Draw}
        }
        \vspace{-.2cm}
        \item{
         \textbf{Languages}{: Python, Javascript, PHP, HTML/CSS, SQL, NoSQL}
        }
        \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------magang sebelumnya-----------------
\section{Employment}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Assistant Lecturer of Fresh Graduate Academy (FGA) by KOMINFO}{Semarang, Indonesia}
      {Diponegoro University}{July 2019 – Aug 2019}
      \resumeItemListStart
        \vspace{-.2cm}
        \item
        {Managed class session and preparing course materials, including syllabi, handouts, and homework assignments.}
        \vspace{-.2cm}
        \resumeItemListEnd
    
     \resumeSubheading
      {Assistant of Microprocessor Engineering Laboratory}{Semarang, Indonesia}
      {Diponegoro University}{Sept 2017 – Dec 2019}
      \resumeItemListStart
        \vspace{-.2cm}
        \item
        {Managed practicum session and exercise project with board Nuvoton NUC140 to hundreds of juniors.}
        \vspace{-.2cm}
        \resumeItemListEnd
        
    \resumeSubheading
      {Software Engineer Intern}{Semarang, Indonesia}
      {Tri-Niche Pte Ltd}{Jan 2019 – Feb 2019}
      \resumeItemListStart
        \vspace{-.2cm}
        \item
        {Work with senior developer to development tasks for front end public and internal websites with framework codeigniter.}
        \vspace{-.2cm}
        \item
        {Collaborate with designers to create clean interfaces and simple website.}
        \vspace{-.2cm}
        \resumeItemListEnd
  \resumeSubHeadingListEnd
  
  %-----------project-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Chatting Yuk!}
      {My personal side project. Series of mobile application focused realtime chat application. Developed everything with React Native, and Firebase.}
    \resumeSubItem{Smart Monitoring and Control System for Hydroponic Plants Based on Android}
      {The movement to create a smarter and efficient hydroponic plants, accelerated by smartphones interacting. This project offers client and to end solution including hardware and software.}
  \resumeSubHeadingListEnd

%
%--------organisasi------------
\section{Leadership Experience}
\resumeSubHeadingListStart
    \resumeSubheading
        {Undip Robotics Development Center} {\emph{Oct 2016 – Mar 2018}}
        {Vice Chairman of Roboboat Team}{}
        \vspace{-.3cm}
    \resumeSubheading
        {Computer Engineering Research Club}{\emph {Apr 2017 – Apr 2019}}
        {Coordinator Laboratory of Robotics and Embedded System }{}
        \vspace{-.3cm}
    \resumeSubheading
        {Computer Engineering Student Association}{\emph {Apr 2017 – Apr 2019}}
        {Vice Chairman of Sport and Art Department}{}
        \vspace{-.3cm}
        
\resumeSubHeadingListEnd

%-----------penghargaan-----------------
\section{Achievements}
\resumeSubHeadingListStart
    \item {\bf [International] Silver Medal Japan Design Idea and Ivention 2019}
    \vspace{-.3cm}
        \resumeItemListStart
            \item {Created an application with categori IoT which got selected in Japan Design Idea and Invention 2019 in Tokyo. The application got selected in final and won silver medal.}
            \vspace{-.3cm}
        \resumeItemListEnd
    \item {\bf [International] Finalist International Roboboat Competition 2018}
    \vspace{-.3cm}
        \resumeItemListStart
            \item {Delegation for International Roboboat Competition at Florida, USA. Was in charge of developing the robot image detection. GUI and robot to server communication.}
        \resumeItemListEnd 
\resumeSubHeadingListEnd

  
% %-----------publication-----------------
% \section{Publication}
%   \resumeSubHeadingListStart
%     \item {\bf Indonesian Sign System (SIBI) Recognition Using Convolutional Neural Network}
%     \vspace{-.3cm}
%         \resumeItemListStart
%             \item {Undergraduate thesis supervised by Dr. Oky Dwi Nurhayati, ST., MT. Accepted and going to appear in the Jurnal Sitem Informasi Bisnis (JSINBIS) 2021.}
%         \resumeItemListEnd 
% \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
